Einstein's gravity from a polynomial affine model

### 2016-05-12 AffGR-PRD.tex
Sent to PRD

\documentclass[aps,prd,12pt,twocolumn,superscriptaddress,showpacs,showkeys,reprint%,longbibliography
]{revtex4-1}

\usepackage{amsmath,amsthm,latexsym,amssymb,amsfonts}
\usepackage{xcolor}
\usepackage[%
  colorlinks=true,
  urlcolor=blue,
  linkcolor=blue,
  citecolor=blue
]{hyperref}
\usepackage{etoolbox}
\usepackage{breqn}

@@

%------------------
%--------- Definitions
%------------------
%% \input{Def-article.tex}
%% \usepackage{mathtools,amsmath,amssymb,amsfonts,dsfont,mathrsfs,amsthm}
%% \usepackage{graphicx}
%% \usepackage{centernot}
%% \usepackage{hyperref}
\usepackage{xcolor}
%% \usepackage{comment}
%% \hypersetup{linktocpage,colorlinks=true,urlcolor=blue!80!red,linkcolor=blue,citecolor=red}
%\usepackage{feynmf}
\usepackage{siunitx}
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
%% \usepackage{ulem}
%\usepackage{tikz}
\usepackage{braket}
\usepackage{xparse}

@@

%% \newcommand{\ket}[1]{\left.\left|#1\right.\right>}
%% \newcommand{\bra}[1]{\left.\left<#1\right.\right|}
\renewcommand\bra[1]{\Bra{#1}}
\renewcommand\ket[1]{\Ket{#1}}
\newcommand{\bkt}[3]{\Braket{ {#1} | {#2} | {#3} } }
\newcommand{\bk}[2]{\Braket{ {#1} | {#2} } }
\newcommand{\comm}[2]{\left[#1,#2\right]}
\newcommand{\acomm}[2]{\left\{#1,#2\right\}}
\newcommand{\vev}[1]{\ensuremath{\left<#1\right>}}
\renewcommand{\set}[1]{\ensuremath{\Set{ #1 }}}

@@

%%%%%%%%% BIBLIOGRAPHY %%%%%%%%%
%% \bibliographystyle{utphys}
\bibliography{References.bib}

>>>>

\documentclass[aps,prd,12pt,twocolumn,superscriptaddress,showpacs,showkeys,reprint,longbibliography
]{revtex4-1}

\usepackage{amsmath,amsthm,latexsym,amssymb,amsfonts}
\usepackage{xcolor}
\usepackage[%
  colorlinks=true,
  urlcolor=blue,
  linkcolor=blue,
  citecolor=blue
]{hyperref}
%\usepackage{etoolbox}
\usepackage{breqn}

@@

%------------------
%--------- Definitions
%------------------
%% \input{Def-article.tex}
%% \usepackage{mathtools,amsmath,amssymb,amsfonts,dsfont,mathrsfs,amsthm}
%% \usepackage{graphicx}
%% \usepackage{centernot}
%% \usepackage{hyperref}
\usepackage{xcolor}
%% \usepackage{comment}
%% \hypersetup{linktocpage,colorlinks=true,urlcolor=blue!80!red,linkcolor=blue,citecolor=red}
%\usepackage{feynmf}
%\usepackage{siunitx}
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
%% \usepackage{ulem}
%\usepackage{tikz}
%\usepackage{braket}
\usepackage{xparse}

@@

%% \newcommand{\ket}[1]{\left.\left|#1\right.\right>}
%% \newcommand{\bra}[1]{\left.\left<#1\right.\right|}
%% \renewcommand\bra[1]{\Bra{#1}}
%% \renewcommand\ket[1]{\Ket{#1}}
\newcommand{\bkt}[3]{\Braket{ {#1} | {#2} | {#3} } }
\newcommand{\bk}[2]{\Braket{ {#1} | {#2} } }
\newcommand{\comm}[2]{\left[#1,#2\right]}
\newcommand{\acomm}[2]{\left\{#1,#2\right\}}
\newcommand{\vev}[1]{\ensuremath{\left<#1\right>}}
%% \renewcommand{\set}[1]{\ensuremath{\Set{ #1 }}}

@@

%%%%%%%%% BIBLIOGRAPHY %%%%%%%%%
%% \bibliographystyle{unsrt}
%% \bibliography{References.bib}
%merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
%Control: key (0)
%Control: author (0) dotless jnrlst
%Control: editor formatted (1) identically to author
%Control: production of article title (0) allowed
%Control: page (1) range
%Control: year (0) verbatim
%Control: production of eprint (0) enabled
\begin{thebibliography}{86}%
\makeatletter
\providecommand \@ifxundefined [1]{%
 \@ifx{#1\undefined}
}%
\providecommand \@ifnum [1]{%
 \ifnum #1\expandafter \@firstoftwo
 \else \expandafter \@secondoftwo
 \fi
}%
\providecommand \@ifx [1]{%
 \ifx #1\expandafter \@firstoftwo
 \else \expandafter \@secondoftwo
 \fi
}%
\providecommand \natexlab [1]{#1}%
\providecommand \enquote  [1]{``#1''}%
\providecommand \bibnamefont  [1]{#1}%
\providecommand \bibfnamefont [1]{#1}%
\providecommand \citenamefont [1]{#1}%
\providecommand \href@noop [0]{\@secondoftwo}%
\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
\providecommand \@href[1]{\@@startlink{#1}\@@href}%
\providecommand \@@href[1]{\endgroup#1\@@endlink}%
\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
\providecommand \@@startlink[1]{}%
\providecommand \@@endlink[0]{}%
\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
\providecommand \urlprefix  [0]{URL }%
\providecommand \Eprint [0]{\href }%
\providecommand \doibase [0]{http://dx.doi.org/}%
\providecommand \selectlanguage [0]{\@gobble}%
\providecommand \bibinfo  [0]{\@secondoftwo}%
\providecommand \bibfield  [0]{\@secondoftwo}%
\providecommand \translation [1]{[#1]}%
\providecommand \BibitemOpen [0]{}%
\providecommand \bibitemStop [0]{}%
\providecommand \bibitemNoStop [0]{.\EOS\space}%
\providecommand \EOS [0]{\spacefactor3000\relax}%
\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
\let\auto@bib@innerbib\@empty
%</preamble>
\bibitem [{\citenamefont {Einstein}(1915)}]{einstein1915feldgleichungen}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Albert}\ \bibnamefont
  {Einstein}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Die
  feldgleichungen der gravitation},}\ }\href@noop {} {\bibfield  {journal}
  {\bibinfo  {journal} {Sitzungsber. preuss. Akad. Wiss.}\ }\textbf {\bibinfo
  {volume} {1}},\ \bibinfo {pages} {844--847} (\bibinfo {year}
  {1915})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Will}(2014)}]{Will:2014kxa}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Clifford~M.}\
  \bibnamefont {Will}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{The
  confrontation between Gerenal Relativity and experiment}},}\ }\href {\doibase
  10.12942/lrr-2014-4} {\bibfield  {journal} {\bibinfo  {journal} {Living Rev.
  Rel.}\ }\textbf {\bibinfo {volume} {17}},\ \bibinfo {pages} {4} (\bibinfo
  {year} {2014})},\ \Eprint {http://arxiv.org/abs/1403.7377} {arXiv:1403.7377
  [gr-qc]} \BibitemShut {NoStop}%
%%CITATION = ARXIV:1002.4928;%%
\bibitem [{\citenamefont {Abbott}\ \emph {et~al.}(2016)\citenamefont {Abbott}
  \emph {et~al.}}]{Abbott:2016blz}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.~P.}\ \bibnamefont
  {Abbott}} \emph {et~al.} (\bibinfo {collaboration} {{Virgo and LIGO
  scientific}}),\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Observation
  of gravitational waves from a binary black hole merger}},}\ }\href {\doibase
  10.1103/PhysRevLett.116.061102} {\bibfield  {journal} {\bibinfo  {journal}
  {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {116}},\ \bibinfo {pages}
  {061102} (\bibinfo {year} {2016})},\ \Eprint
  {http://arxiv.org/abs/1602.03837} {arXiv:1602.03837 [gr-qc]} \BibitemShut
  {NoStop}%
%%CITATION = ARXIV:1602.03837;%%
\bibitem [{\citenamefont {Cartan}(1922)}]{Cartan1922}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Elie}\ \bibnamefont
  {Cartan}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Sur une
  g\'en\'eralisation de la notion de courbure de riemann et les espaces \`a
  torsion},}\ }\href {http://gallica.bnf.fr/ark:/12148/bpt6k3127j.image.langFR}
  {\bibfield  {journal} {\bibinfo  {journal} {C. R. Acad. Sci. Paris}\ }\textbf
  {\bibinfo {volume} {174}},\ \bibinfo {pages} {593} (\bibinfo {year}
  {1922})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Cartan}(1923)}]{Cartan1923}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Elie}\ \bibnamefont
  {Cartan}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Sur les
  vari{\'e}t{\'e}s {\`a} connexion affine et la th{\'e}orie de la
  relativit{\'e} g{\'e}n{\'e}ralis{\'e}e (premi{\`e}re partie)},}\ }\href
  {http://archive.numdam.org/article/ASENS_1923_3_40__325_0.pdf} {\bibfield
  {journal} {\bibinfo  {journal} {Ann. Ec. Norm. Super.}\ }\textbf {\bibinfo
  {volume} {40}},\ \bibinfo {pages} {325} (\bibinfo {year} {1923})}\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Cartan}(1924)}]{Cartan1924}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Elie}\ \bibnamefont
  {Cartan}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Sur les
  vari\'et\'es \`a connexion affine, et la th\'eorie de la relativit\'e
  g\'en\'eralis\'ee (premi\`ere partie) (suite)},}\ }\href
  {http://www.numdam.org/numdam-bin/item?id=ASENS_1924_3_41__1_0} {\bibfield
  {journal} {\bibinfo  {journal} {Ann. Ec. Norm. Super.}\ }\textbf {\bibinfo
  {volume} {41}},\ \bibinfo {pages} {1} (\bibinfo {year} {1924})}\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Cartan}(1925)}]{Cartan1925}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Elie}\ \bibnamefont
  {Cartan}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Sur les
  vari\'et\'es \`a connexion affine et la th\'eorie de la relativit\'e
  g\'en\'eralis\'ee, part ii,},}\ }\href
  {http://www.numdam.org/numdam-bin/item?id=ASENS_1925_3_42__17_0} {\bibfield
  {journal} {\bibinfo  {journal} {Ann. Ec. Norm. Super.}\ }\textbf {\bibinfo
  {volume} {42}},\ \bibinfo {pages} {17} (\bibinfo {year} {1925})}\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {'t~Hooft}(1973)}]{'tHooft:1973us}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Gerard}\ \bibnamefont
  {'t~Hooft}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{An algorithm
  for the poles at dimension four in the dimensional regularization
  procedure}},}\ }\href {\doibase 10.1016/0550-3213(73)90263-0} {\bibfield
  {journal} {\bibinfo  {journal} {Nucl. Phys. B}\ }\textbf {\bibinfo {volume}
  {62}},\ \bibinfo {pages} {444} (\bibinfo {year} {1973})}\BibitemShut
  {NoStop}%
%%CITATION = NUPHA,B62,444;%%
\bibitem [{\citenamefont {'t~Hooft}\ and\ \citenamefont
  {Veltman}(1974)}]{'tHooft:1974bx}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Gerard}\ \bibnamefont
  {'t~Hooft}}\ and\ \bibinfo {author} {\bibfnamefont {M.~J.~G.}\ \bibnamefont
  {Veltman}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{One loop
  divergencies in the theory of gravitation}},}\ }\href@noop {} {\bibfield
  {journal} {\bibinfo  {journal} {Annales Poincare Phys. Theor. A}\ }\textbf
  {\bibinfo {volume} {20}},\ \bibinfo {pages} {69} (\bibinfo {year}
  {1974})}\BibitemShut {NoStop}%
%%CITATION = AHPAA,A20,69;%%
\bibitem [{\citenamefont {Deser}\ and\ \citenamefont {van
  Nieuwenhuizen}(1974{\natexlab{a}})}]{Deser:1974cz}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Stanley}\ \bibnamefont
  {Deser}}\ and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {van
  Nieuwenhuizen}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{One Loop
  Divergences of Quantized Einstein-Maxwell Fields}},}\ }\href {\doibase
  10.1103/PhysRevD.10.401} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
  Rev. D}\ }\textbf {\bibinfo {volume} {10}},\ \bibinfo {pages} {401} (\bibinfo
  {year} {1974}{\natexlab{a}})}\BibitemShut {NoStop}%
%%CITATION = PHRVA,D10,401;%%
\bibitem [{\citenamefont {Deser}\ and\ \citenamefont {van
  Nieuwenhuizen}(1974{\natexlab{b}})}]{Deser:1974cy}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Stanley}\ \bibnamefont
  {Deser}}\ and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {van
  Nieuwenhuizen}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
  {{Nonrenormalizability of the Quantized Dirac-Einstein System}},}\ }\href
  {\doibase 10.1103/PhysRevD.10.411} {\bibfield  {journal} {\bibinfo  {journal}
  {Phys. Rev. D}\ }\textbf {\bibinfo {volume} {10}},\ \bibinfo {pages} {411}
  (\bibinfo {year} {1974}{\natexlab{b}})}\BibitemShut {NoStop}%
%%CITATION = PHRVA,D10,411;%%
\bibitem [{\citenamefont {Arnowitt}\ \emph {et~al.}(1959)\citenamefont
  {Arnowitt}, \citenamefont {Deser},\ and\ \citenamefont
  {Misner}}]{Arnowitt:1959ah}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Richard~L.}\
  \bibnamefont {Arnowitt}}, \bibinfo {author} {\bibfnamefont {Stanley}\
  \bibnamefont {Deser}}, \ and\ \bibinfo {author} {\bibfnamefont {Charles~W.}\
  \bibnamefont {Misner}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
  {{Dynamical Structure and Definition of Energy in General Relativity}},}\
  }\href {\doibase 10.1103/PhysRev.116.1322} {\bibfield  {journal} {\bibinfo
  {journal} {Phys. Rev.}\ }\textbf {\bibinfo {volume} {116}},\ \bibinfo {pages}
  {1322} (\bibinfo {year} {1959})}\BibitemShut {NoStop}%
%%CITATION = PHRVA,116,1322;%%
\bibitem [{\citenamefont {Arnowitt}\ \emph {et~al.}(1960)\citenamefont
  {Arnowitt}, \citenamefont {Deser},\ and\ \citenamefont
  {Misner}}]{Arnowitt:1960es}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Richard~L.}\
  \bibnamefont {Arnowitt}}, \bibinfo {author} {\bibfnamefont {Stanley}\
  \bibnamefont {Deser}}, \ and\ \bibinfo {author} {\bibfnamefont {Charles~W.}\
  \bibnamefont {Misner}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
  {{Canonical variables for general relativity}},}\ }\href {\doibase
  10.1103/PhysRev.117.1595} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
  Rev.}\ }\textbf {\bibinfo {volume} {117}},\ \bibinfo {pages} {1595} (\bibinfo
  {year} {1960})}\BibitemShut {NoStop}%
%%CITATION = PHRVA,117,1595;%%
\bibitem [{\citenamefont {Wheeler}(1964)}]{WheelerGeo}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {John~A.}\ \bibnamefont
  {Wheeler}},\ }\enquote {\bibinfo {title} {{R}elativity, groups and
  topology},}\ \ (\bibinfo  {publisher} {Gordon and Breach},\ \bibinfo {year}
  {1964})\ Chap.\ \bibinfo {chapter} {{G}eometrodynamics and the issue of the
  final state}, p.\ \bibinfo {pages} {317}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {DeWitt}(1967{\natexlab{a}})}]{DeWitt:1967yk}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Bryce~S.}\
  \bibnamefont {DeWitt}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
  {{Quantum Theory of Gravity. 1. The Canonical Theory}},}\ }\href {\doibase
  10.1103/PhysRev.160.1113} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
  Rev.}\ }\textbf {\bibinfo {volume} {160}},\ \bibinfo {pages} {1113} (\bibinfo
  {year} {1967}{\natexlab{a}})}\BibitemShut {NoStop}%
%%CITATION = PHRVA,160,1113;%%
\bibitem [{\citenamefont {DeWitt}(1967{\natexlab{b}})}]{DeWitt:1967ub}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Bryce~S.}\
  \bibnamefont {DeWitt}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
  {{Quantum Theory of Gravity. 2. The Manifestly Covariant Theory}},}\ }\href
  {\doibase 10.1103/PhysRev.162.1195} {\bibfield  {journal} {\bibinfo
  {journal} {Phys. Rev.}\ }\textbf {\bibinfo {volume} {162}},\ \bibinfo {pages}
  {1195} (\bibinfo {year} {1967}{\natexlab{b}})}\BibitemShut {NoStop}%
%%CITATION = PHRVA,162,1195;%%
\bibitem [{\citenamefont {DeWitt}(1967{\natexlab{c}})}]{DeWitt:1967uc}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Bryce~S.}\
  \bibnamefont {DeWitt}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
  {{Quantum Theory of Gravity. 3. Applications of the Covariant Theory}},}\
  }\href {\doibase 10.1103/PhysRev.162.1239} {\bibfield  {journal} {\bibinfo
  {journal} {Phys. Rev.}\ }\textbf {\bibinfo {volume} {162}},\ \bibinfo {pages}
  {1239} (\bibinfo {year} {1967}{\natexlab{c}})}\BibitemShut {NoStop}%
%%CITATION = PHRVA,162,1239;%%
\bibitem [{\citenamefont {Gambini}\ and\ \citenamefont
  {Trias}(1981)}]{Gambini:1980yz}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
  {Gambini}}\ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {Trias}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{On the
  Geometrical Origin of Gauge Theories}},}\ }\href {\doibase
  10.1103/PhysRevD.23.553} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
  Rev. D}\ }\textbf {\bibinfo {volume} {23}},\ \bibinfo {pages} {553} (\bibinfo
  {year} {1981})}\BibitemShut {NoStop}%
%%CITATION = PHRVA,D23,553;%%
\bibitem [{\citenamefont {Gambini}\ and\ \citenamefont
  {Trias}(1986)}]{Gambini:1986ew}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Rodolfo}\ \bibnamefont
  {Gambini}}\ and\ \bibinfo {author} {\bibfnamefont {Antoni}\ \bibnamefont
  {Trias}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Gauge Dynamics
  in the C Representation}},}\ }\href {\doibase 10.1016/0550-3213(86)90221-X}
  {\bibfield  {journal} {\bibinfo  {journal} {Nucl. Phys. B}\ }\textbf
  {\bibinfo {volume} {278}},\ \bibinfo {pages} {436} (\bibinfo {year}
  {1986})}\BibitemShut {NoStop}%
%%CITATION = NUPHA,B278,436;%%
\bibitem [{\citenamefont {Ashtekar}(1986)}]{Ashtekar:1986yd}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {Ashtekar}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{New Variables
  for Classical and Quantum Gravity}},}\ }\href {\doibase
  10.1103/PhysRevLett.57.2244} {\bibfield  {journal} {\bibinfo  {journal}
  {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {57}},\ \bibinfo {pages}
  {2244--2247} (\bibinfo {year} {1986})}\BibitemShut {NoStop}%
%%CITATION = PRLTA,57,2244;%%
\bibitem [{\citenamefont {Ashtekar}(1987)}]{Ashtekar:1987gu}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {Ashtekar}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{New
  Hamiltonian Formulation of General Relativity}},}\ }\href {\doibase
  10.1103/PhysRevD.36.1587} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
  Rev. D}\ }\textbf {\bibinfo {volume} {36}},\ \bibinfo {pages} {1587}
  (\bibinfo {year} {1987})}\BibitemShut {NoStop}%
%%CITATION = PHRVA,D36,1587;%%
\bibitem [{\citenamefont {Holst}(1996)}]{Holst:1995pc}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Soren}\ \bibnamefont
  {Holst}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Barbero's
  Hamiltonian derived from a generalized Hilbert-Palatini action}},}\ }\href
  {\doibase 10.1103/PhysRevD.53.5966} {\bibfield  {journal} {\bibinfo
  {journal} {Phys. Rev. D}\ }\textbf {\bibinfo {volume} {53}},\ \bibinfo
  {pages} {5966} (\bibinfo {year} {1996})},\ \Eprint
  {http://arxiv.org/abs/gr-qc/9511026} {arXiv:gr-qc/9511026 [gr-qc]}
  \BibitemShut {NoStop}%
%%CITATION = GR-QC/9511026;%%
\bibitem [{\citenamefont {Kibble}(1961)}]{Kibble:1961ba}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.~W.~B.}\
  \bibnamefont {Kibble}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
  {{Lorentz invariance and the gravitational field}},}\ }\href {\doibase
  10.1063/1.1703702} {\bibfield  {journal} {\bibinfo  {journal} {J. Math.
  Phys.}\ }\textbf {\bibinfo {volume} {2}},\ \bibinfo {pages} {212--221}
  (\bibinfo {year} {1961})}\BibitemShut {NoStop}%
%%CITATION = JMAPA,2,212;%%
\bibitem [{\citenamefont {Hehl}\ \emph {et~al.}(1976)\citenamefont {Hehl},
  \citenamefont {von~der Heyde}, \citenamefont {Kerlick},\ and\ \citenamefont
  {Nester}}]{Hehl:1976kj}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Friedrich~W.}\
  \bibnamefont {Hehl}}, \bibinfo {author} {\bibfnamefont {Paul}\ \bibnamefont
  {von~der Heyde}}, \bibinfo {author} {\bibfnamefont {G.~David}\ \bibnamefont
  {Kerlick}}, \ and\ \bibinfo {author} {\bibfnamefont {James~M.}\ \bibnamefont
  {Nester}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {General
  relativity with spin and torsion: Foundations and prospects},}\ }\href
  {\doibase 10.1103/RevModPhys.48.393} {\bibfield  {journal} {\bibinfo
  {journal} {Rev. Mod. Phys.}\ }\textbf {\bibinfo {volume} {48}},\ \bibinfo
  {pages} {393} (\bibinfo {year} {1976})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Shapiro}(2002)}]{Shapiro:2001rz}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.~L.}\ \bibnamefont
  {Shapiro}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Physical
  aspects of the space-time torsion}},}\ }\href {\doibase
  10.1016/S0370-1573(01)00030-8} {\bibfield  {journal} {\bibinfo  {journal}
  {Phys. Rep.}\ }\textbf {\bibinfo {volume} {357}},\ \bibinfo {pages} {113}
  (\bibinfo {year} {2002})},\ \Eprint {http://arxiv.org/abs/hep-th/0103093}
  {arXiv:hep-th/0103093 [hep-th]} \BibitemShut {NoStop}%
%%CITATION = HEP-TH/0103093;%%
\bibitem [{\citenamefont {Hammond}(2002)}]{Hammond:2002rm}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~T.}\ \bibnamefont
  {Hammond}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Torsion
  gravity}},}\ }\href {\doibase 10.1088/0034-4885/65/5/201} {\bibfield
  {journal} {\bibinfo  {journal} {Rept. Prog. Phys.}\ }\textbf {\bibinfo
  {volume} {65}},\ \bibinfo {pages} {599} (\bibinfo {year} {2002})}\BibitemShut
  {NoStop}%
%%CITATION = RPPHA,65,599;%%
\bibitem [{\citenamefont {Hehl}\ \emph {et~al.}(1995)\citenamefont {Hehl},
  \citenamefont {McCrea}, \citenamefont {Mielke},\ and\ \citenamefont
  {Ne'eman}}]{Hehl:1994ue}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Friedrich~W.}\
  \bibnamefont {Hehl}}, \bibinfo {author} {\bibfnamefont {J.~Dermott}\
  \bibnamefont {McCrea}}, \bibinfo {author} {\bibfnamefont {Eckehard~W.}\
  \bibnamefont {Mielke}}, \ and\ \bibinfo {author} {\bibfnamefont {Yuval}\
  \bibnamefont {Ne'eman}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
  {{Metric affine gauge theory of gravity: Field equations, Noether identities,
  world spinors, and breaking of dilation invariance}},}\ }\href {\doibase
  10.1016/0370-1573(94)00111-F} {\bibfield  {journal} {\bibinfo  {journal}
  {Phys. Rep.}\ }\textbf {\bibinfo {volume} {258}},\ \bibinfo {pages} {1--171}
  (\bibinfo {year} {1995})},\ \Eprint {http://arxiv.org/abs/gr-qc/9402012}
  {arXiv:gr-qc/9402012 [gr-qc]} \BibitemShut {NoStop}%
%%CITATION = GR-QC/9402012;%%
\bibitem [{\citenamefont {Pagani}\ and\ \citenamefont
  {Percacci}(2015)}]{Pagani:2015ema}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Carlo}\ \bibnamefont
  {Pagani}}\ and\ \bibinfo {author} {\bibfnamefont {Roberto}\ \bibnamefont
  {Percacci}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Quantum
  gravity with torsion and non-metricity}},}\ }\href {\doibase
  10.1088/0264-9381/32/19/195019} {\bibfield  {journal} {\bibinfo  {journal}
  {Class. Quant. Grav.}\ }\textbf {\bibinfo {volume} {32}},\ \bibinfo {pages}
  {195019} (\bibinfo {year} {2015})},\ \Eprint
  {http://arxiv.org/abs/1506.02882} {arXiv:1506.02882 [gr-qc]} \BibitemShut
  {NoStop}%
%%CITATION = ARXIV:1506.02882;%%
\bibitem [{\citenamefont {Sezgin}\ and\ \citenamefont {van
  Nieuwenhuizen}(1980)}]{Sezgin:1979zf}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
  {Sezgin}}\ and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {van
  Nieuwenhuizen}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{New Ghost
  Free Gravity Lagrangians with Propagating Torsion}},}\ }\href {\doibase
  10.1103/PhysRevD.21.3269} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
  Rev. D}\ }\textbf {\bibinfo {volume} {21}},\ \bibinfo {pages} {3269}
  (\bibinfo {year} {1980})}\BibitemShut {NoStop}%
%%CITATION = PHRVA,D21,3269;%%
\bibitem [{\citenamefont {Mannheim}\ and\ \citenamefont
  {Davidson}(2005)}]{Mannheim:2004qz}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Philip~D.}\
  \bibnamefont {Mannheim}}\ and\ \bibinfo {author} {\bibfnamefont {Aharon}\
  \bibnamefont {Davidson}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
  {{Dirac quantization of the Pais-Uhlenbeck fourth order oscillator}},}\
  }\href {\doibase 10.1103/PhysRevA.71.042110} {\bibfield  {journal} {\bibinfo
  {journal} {Phys. Rev. A}\ }\textbf {\bibinfo {volume} {71}},\ \bibinfo
  {pages} {042110} (\bibinfo {year} {2005})},\ \Eprint
  {http://arxiv.org/abs/hep-th/0408104} {arXiv:hep-th/0408104 [hep-th]}
  \BibitemShut {NoStop}%
%%CITATION = HEP-TH/0408104;%%
\bibitem [{\citenamefont {Bender}\ and\ \citenamefont
  {Mannheim}(2008{\natexlab{a}})}]{Bender:2007wu}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Carl~M.}\ \bibnamefont
  {Bender}}\ and\ \bibinfo {author} {\bibfnamefont {Philip~D.}\ \bibnamefont
  {Mannheim}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{No-ghost
  theorem for the fourth-order derivative Pais-Uhlenbeck oscillator model}},}\
  }\href {\doibase 10.1103/PhysRevLett.100.110402} {\bibfield  {journal}
  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {100}},\
  \bibinfo {pages} {110402} (\bibinfo {year} {2008}{\natexlab{a}})},\ \Eprint
  {http://arxiv.org/abs/0706.0207} {arXiv:0706.0207 [hep-th]} \BibitemShut
  {NoStop}%
%%CITATION = ARXIV:0706.0207;%%
\bibitem [{\citenamefont {Smilga}(2009)}]{Smilga:2008pr}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~V.}\ \bibnamefont
  {Smilga}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Comments on the
  dynamics of the Pais-Uhlenbeck oscillator}},}\ }\bibfield  {booktitle} {\emph
  {\bibinfo {booktitle} {{Proceedings, 7th Workshop on Quantum Physics with
  Non-Hermitian Operators (PHHQP VII)}}},\ }\href {\doibase
  10.3842/Sigma.2009.017} {\bibfield  {journal} {\bibinfo  {journal} {SIGMA}\
